---
title: "Soil"
author: "jjh"
editor: visual
---

```{r, include = FALSE}
require(tidyverse)
require(foreign)
require(ggplot2)
require(MASS)
require(multcompView)
require(car)
require(ggsignif)
```

# April 4, 2023

```{r}
soil <- read.csv('soil_main.csv') %>%
  as_tibble() %>%
    mutate_at(vars(material, depth_mean, depth_cat), factor)
```

```{r}
soil
```

# Linear regression - no transformation

```{r}
soil.lm <- lm(mbc ~ depth_cat * material, data = soil)
```

# Model assumption
# Asumptions are not valid for simple linear regression
# Residuals are not equally or independently distributed

```{r}
par(mfrow = c(2, 2))
plot(soil.lm)
```

# Log-transformation
# Although outliers are present, log-transform of the response variable, mbc, appear to meet the #assumptions of simplae linear regression 

```{r}
soil_log.lm <- lm(log(mbc) ~ depth_cat * material, data = soil)
```

```{r}
par(mfrow = c(2, 2))
plot(soil_log.lm)
```

```{r}
summary(soil_log.lm)
```

# car package

```{r}
Anova(soil_log.lm)
```

# Just depth as a predictor variable

```{r}
soil_log2.lm <- lm(log(mbc) ~ material + depth_cat, data = soil)
```

```{r}
par(mfrow = c(2, 2))
plot(soil_log2.lm)
```

```{r}
summary(soil_log2.lm)
```

```{r}
Anova(soil_log2.lm)
```

# ANOVA model with "aov"

```{r}
soil_log2.aov <- aov(log(mbc) ~ material + depth_cat, data = soil)
```

```{r}
summary(soil_log2.aov)
```

# Tukey HSD test

```{r}
tukey <- TukeyHSD(soil_log2.aov)
```

```{r}
tukey
```

# cld

```{r}
cld <- multcompLetters4(soil_log2.aov, tukey) 
```

```{r}
cld
```
```{r}
cld$depth_cat
```

# Table

```{r}
data_summary <- soil %>%
    mutate_at(vars(material, depth_range, depth_cat), factor) %>%
    group_by(material, depth_cat) %>%
  dplyr::summarize(mean = mean(mbc), 
                   sd = sd(mbc), 
                   n = n(),
                   se = sd/sqrt(n)) %>%
  arrange(desc(mean))
```

```{r}
data_summary
```

```{r}
soil_main <- read.csv('soil_main.csv') %>%
  as_tibble() %>%
  mutate_at(vars(material, depth_cat), factor) %>%
  group_by(material, depth_cat) %>%
  dplyr::summarize(mean = mean(mbc), 
                   sd = sd(mbc), 
                   n = n(),
                   se = sd/sqrt(n)
  ) %>%
  mutate(se = sd / sqrt(n),
         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se)
```

```{r}
soil_main
```

```{r}
x_labels = c("1", "2", "3", "4", "5", "6", "7", "8")
```

```{r}
x_labels2 = c("0-11", "11-26", "26-38", "38-54", "54-67", "67-81", "81-96", "96-111")
```

```{r}
soil_main.barplot <- ggplot(soil_main, aes(x = depth_cat, y = mean, fill = material)) +   
  geom_bar(stat = "identity", position = position_dodge(width = 0.9), width = 0.75, color = "#2b2b2b", linewidth = 0.50, alpha = 0.6) +
  geom_linerange(aes(ymin = mean, ymax = mean + se), position = position_dodge(width = 0.9), linewidth = 0.75) +
  #geom_signif(comparisons = list(c("1", "1")), y_position = 9950,
  #            tip_length = 0, vjust = 0.1) +
  geom_signif(comparisons = list(c("2", "8")), y_position = 5250,
              annotation = c("B"),
              tip_length = 0, vjust = 0.1) +
  #scale_y_discrete(expand = c(0, 8000), expression(paste("mbc"))) + 
  scale_x_discrete(expand = c(0, 1), labels = x_labels2) + 
  ggtitle(expression(paste(italic(" Soil")))) +
  ylab(expression(paste("mbc"))) +
  ylim(0, 10000) +
  labs(x = NULL) +
  theme(strip.text = element_text(size = 10, color = "black", hjust = 0.50),
        strip.background = element_rect(fill = "#FFFFFF", color = NA),    
        panel.background = element_rect(fill = "#FFFFFF", color = NA),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_line(color = "#b2b2b2"),
        panel.spacing.x = unit(1, "cm"),
        panel.spacing.y = unit(0.5, "cm"),
        panel.spacing = unit(1, "lines"),
        axis.ticks = element_blank(),
        legend.position = "right",
        plot.title = element_text(size = 11),
        axis.title.y = element_text(size = 11),
        legend.title = element_blank())
```

```{r}
soil_main.barplot
```

# Log-transformed summary

```{r}
soil_log_main <- read.csv('soil_main.csv') %>%
  as_tibble() %>%
  mutate_at(vars(material, depth_cat), factor) %>%
  group_by(material, depth_cat) %>%
  dplyr::summarize(mean = mean(log(mbc)), 
                   sd = sd(log(mbc)), 
                   n = n(),
                   se = sd/sqrt(n)
  ) %>%
  mutate(se = sd / sqrt(n),
         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se)
```

```{r}
soil_log_main
```

# Add Letters for significance

```{r}
soil_log_main.barplot <- ggplot(soil_log_main, aes(x = depth_cat, y = mean, fill = material)) +   
  geom_bar(stat = "identity", position = position_dodge(width = 0.9), width = 0.75, color = "#2b2b2b", linewidth = 0.50, alpha = 0.6) +
  geom_linerange(aes(ymin = mean, ymax = mean + se), position = position_dodge(width = 0.9), linewidth = 0.75) +
  #geom_signif(comparisons = list(c("1", "1")), y_position = 9950,
  #            tip_length = 0, vjust = 0.1) +
  geom_signif(comparisons = list(c("2", "8")), y_position = 8.0,
              annotation = c("B"),
              tip_length = 0, vjust = 0.1) +
  scale_x_discrete(expand = c(0, 1), labels = x_labels2) + 
  ggtitle(expression(paste(italic(" Soil")))) +
  ylab(expression(paste("mbc (log-transformed)"))) +
  ylim(0, 10) +
  labs(x = NULL) +
  theme(strip.text = element_text(size = 10, color = "black", hjust = 0.50),
        strip.background = element_rect(fill = "#FFFFFF", color = NA),    
        panel.background = element_rect(fill = "#FFFFFF", color = NA),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_line(color = "#b2b2b2"),
        panel.spacing.x = unit(1, "cm"),
        panel.spacing.y = unit(0.5, "cm"),
        panel.spacing = unit(1, "lines"),
        axis.ticks = element_blank(),
        legend.position = "right",
        plot.title = element_text(size = 11),
        axis.title.y = element_text(size = 11),
        legend.title = element_blank())
```

```{r}
soil_log_main.barplot
```
