---
title: "Supplementary Material II"
author: "James J. Herlan"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y %H:%M')`"
format: pdf
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(betareg)
library(plyr)
library(lmtest)
library(glmmTMB)
library(boot)
library(emmeans)
library(brms)
library(mvtnorm)
library(nlme)
library(rstan)
library(lmtest)
library(boot)
library(car)
library(xtable)
library(tidyr)
library(ordinal)
library(VGAM)
library(mosaic)  
library(arm)
library(cowplot)
library(qqtest)  #for uncertainty intervals in qqplot
library(modelsummary)
library(kableExtra)
library(gt)
require(MASS)
require(tinytex)

require(tidyverse)
require(plyr)
require(betareg)
require(lmtest)
require(glmmTMB)
require(boot)
require(emmeans)
require(brms)
require(mvtnorm)
require(nlme)
require(rstan)
require(VGAM)
require(car)
require(lme4)
require(Rmisc)
require(readr)
require(multcomp)
require(ggthemes)
require(multcompView)
require(flextable)
```

### Colony Size

```{r}
poci_size <- read.csv('coral_size.csv')
```

```{r}
poci_size.gg <- read_csv("poci_size_main.csv")
```

```{r}
ggplot(poci_size.gg, aes(x = size_cm)) +
  geom_histogram(fill = "#333399") + 
  #below here is ylabel, xlabel, and main title
  ylab("Frequency") +
  xlab(NULL) +
  ggtitle(expression("Coral size " (cm**2))) +
  theme_bw() +
  facet_wrap(~ Site, ncol = 1) +
  #theme sets sizes, text, etc
  theme(axis.title.x = element_text(size = 14), 
        axis.title.y = element_text(size = 14), 
        axis.text.y  = element_text(size= 10),
        axis.text.x  = element_text(size = 12), 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 14),
        # change plot background, grid lines, etc (just examples so you can see)
        panel.background = element_rect(fill = "white"),
        panel.grid.minor.y = element_blank(),
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "white"),
        legend.background = element_rect(fill = "white"),
        strip.text.x = element_text(size = 12, colour = "#FFFFFF"),
        strip.background = element_rect(fill = '#000066')
  )
```

```{r}
poci_size2 <-
poci_size %>%
  as_tibble() %>%
  mutate(size_cm = area*10000) %>%
  group_by(Site) %>%
  dplyr::summarize(mean = mean(size_cm), 
                   sd = sd(size_cm), 
                   n = n(),
                   se = sd/sqrt(n)
  ) %>%
  mutate(se = sd / sqrt(n),
         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  mutate_at(vars(Site), factor) %>%
  add_column(
          location = c('Anakena', 'Manavai', 'Southeast')
          ) %>%
  mutate_at(vars(location), factor)
```

```{r}
poci_size2
```

```{r}
poci_size.gg <-
  poci_size %>%
  mutate(size_cm = area*10000) %>%
  as_tibble() %>%
  mutate_at(vars(Site), factor)
```

```{r}
poci_size.gg
```

```{r}
model_1.lm <- lm(size_cm ~ Site, data = poci_size.gg)
```

```{r}
model_1.lm
```

```{r}
summary(model_1.lm)
```

```{r}
par(mfrow = c(2, 2))
plot(model_1.lm)
```

```{r}
Anova(model_1.lm, type = "III")
```

```{r}
model_1.aov <- Anova(model_1.lm, type = "III")
```

```{r}
as.data.frame(model_1.aov)
```

```{r}
flextable(model_1.aov)
```

```{r}
post_hoc.model_1.lm <- glht(model_1.lm, linfct = mcp(Site = 'Tukey'))
```

```{r}
model_1.aov <- aov(size_cm ~ Site, data = poci_size.gg)
```

```{r}
# Tukey's test
tukey <- TukeyHSD(model_1.aov)
```

```{r}
# compact letter display
cld <- multcompLetters4(model_1.aov, tukey)
```

```{r}
cld
```

```{r}
poci_size3 <- 
poci_size2 %>%
  add_column(
          cld = c('a', 'b', 'c')
          ) %>%
mutate_at(vars(cld), factor)
```

```{r}
poci_size3
```

### Percent Cover

*From* **Damgaard & Irvine (2019)** Using the beta distribution to analyse plant cover data *Journal of Ecology. 107:2747-2759*

```{r, include = TRUE}
p_cover = read_csv('rpn_percent_cover.csv') %>% 
  group_by(Site) %>%
  mutate(
    pland_decimal = pland*0.01
  ) %>%
  mutate_at(vars(Site, cover, plot_id), factor)
```

```{r}
p_cover
```

```{r}
head(p_cover)
```

```{r}
ggplot(p_cover, aes(x = pland_decimal)) +
  geom_histogram(fill = "#333399") + 
  #below here is ylabel, xlabel, and main title
  ylab("Frequency") +
  xlab(NULL) +
  ggtitle(expression("Coral Cover (%)")) +
  theme_bw() +
  facet_wrap(~ Site, ncol = 1) +
  #theme sets sizes, text, etc
  theme(axis.title.x = element_text(size = 14), 
        axis.title.y = element_text(size = 14), 
        axis.text.y  = element_text(size= 10),
        axis.text.x  = element_text(size = 12), 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 14),
        # change plot background, grid lines, etc (just examples so you can see)
        panel.background = element_rect(fill = "white"),
        panel.grid.minor.y = element_blank(),
        panel.grid.major = element_blank(),
        plot.background = element_rect(fill = "white"),
        legend.background = element_rect(fill = "white"),
        strip.text.x = element_text(size = 12, colour = "#FFFFFF"),
        strip.background = element_rect(fill = '#000066')
  )
```

```{r}
plot(pland_decimal ~ Site, data = p_cover)
```

```{r}
p_cover.mean <-
  p_cover %>%
  group_by(Site) %>%
  dplyr::summarise(mean = mean(pland_decimal))
```

```{r}
p_cover.mean
```

## Methods for analyzing percent cover of pocilloporid coral

One option for dealing with the 0 and 1 values is to transform them to be slightly less than one or more than zero. This approach assumes that the data are consistent with a common beta distribution. We fit five models to the data: three variations on the beta model and two linear model approaches.

A beta regression assuming a common spatial aggregation $\delta$ or precision parameter ($\phi$) (object named: mod.beta1). Notice that $\delta= \frac{1}{1+\phi}$ and $\phi=\frac{(1-\delta)}{\delta}$. A beta regression assuming each reef location had a different $\phi$ parameter.

Other options based on assuming that the residuals are normally distributed is to use a linear model with a logit-transformed response or a linear model with response untransformed proportions.

For comparison this applies a logit-transformation to the empirical proportions and then uses a standard linear regression model.

**Raw data - no transformation**

```{r}
p_cover_mod.aov1 <- aov(pland_decimal ~ Site, data = p_cover)
summary(p_cover_mod.aov1)
```

```{r}
p_cover_mod.lm1 <- lm(pland_decimal ~ Site, data = p_cover)
summary(p_cover_mod.lm1)
```

```{r}
par(mfrow = c(2, 2))
plot(p_cover_mod.lm1)
```

```{r}
Anova(p_cover_mod.lm1, type = "III")
```

One option to deal with 0 and 100 percent cover is to add and subtract a small amount to those values

```{r}
transform01 <- function(x) {
  (x * (length(x) - 1) + 0.5) / (length(x))
}
```

```{r}
p_cover$pland_decimal_scaled <- transform01(p_cover$pland_decimal)
```

**Logit-transformation**

```{r}
p_cover_mod.lm2 <- lm(logit(pland_decimal_scaled) ~ Site, data = p_cover) 
```

```{r}
summary(p_cover_mod.lm2)
```

```{r}
par(mfrow = c(2, 2))
plot(p_cover_mod.lm2)
```

```{r}
Anova(p_cover_mod.lm2, type = "III")
```

**Generalized-linear model**

```{r}
p_cover_mod.glm1 <- glm(pland_decimal ~ Site, family = binomial, data = p_cover)
summary(p_cover_mod.glm1)
```

```{r}
par(mfrow = c(2, 2))
plot(p_cover_mod.glm1)
```

```{r}
Anova(p_cover_mod.glm1, type = "III")
```

**Beta Regression I:** $\phi$ does not vary

```{r}
p_cover_mod.beta1 <- betareg(pland_decimal_scaled ~ Site, data = p_cover, link = c("logit"), link.phi = NULL, type = c("ML"))
```

```{r}
summary(p_cover_mod.beta1)
```

**Beta Regression II:** $\phi$ does vary (by **Site**)

```{r}
p_cover_mod.beta2 <- betareg(pland_decimal_scaled ~ Site | Site, data = p_cover, link = c("logit"), link.phi = NULL, type = c("ML"))
```

**Extract AIC from beta regression models**

```{r}
p_cover_mod.beta1_aic <- AIC(p_cover_mod.beta1)
p_cover_mod.beta2_aic <- AIC(p_cover_mod.beta2)
```

```{r}
p_cover_mod.beta1_aic
p_cover_mod.beta2_aic
```
