---
title: "Percent Cover and Bleaching in 2015"
author: "jjh"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y %H:%M')`"
editor: visual
---

```{r, include = FALSE}
require(tidyverse)
require(plyr)
require(betareg)
require(lmtest)
require(glmmTMB)
require(boot)
require(emmeans)
require(brms)
require(mvtnorm)
require(nlme)
require(rstan)
require(VGAM)
require(Rmisc)
require(car)
require(multcomp)
```

```{r, incluse = FALSE}
rpn_bleach <- read.csv('rpn_bleach_2015.csv') %>%
  as_tibble() %>%
  mutate_at(vars(location, depth, transect, group, status), factor)
```

```{r}
rpn_summary <- rpn_bleach %>%  
  group_by(location, depth, transect, group) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_PLOB <- rpn_bleach %>%  
  filter(group == "PLOB") %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_plob <- read.csv('rpn_cover.csv') %>%
  as_tibble() %>%
  filter(group == "PLOB") %>%
  mutate_at(vars(location, depth, transect, group), factor) %>%
  mutate(
  cover = total_count/total_points,
  failures = total_points - total_count
    )
```

```{r, inlcude = FALSE}
rpn_plob
```

## Porites 
### Generalized linear model

```{r}
plob.glm <- glm(cbind(total_count, failures) ~ location * depth, 
                    family = binomial(link = "logit"), 
                    data = rpn_plob)
```

```{r}
par(mfrow = c(2, 2))
plot(plob.glm)
```

```{r}
summary(plob.glm)
```

#### https://www.rpubs.com/daharo_calpoly/502695

```{r}
rpn_plob$groups <- interaction(rpn_plob$location, rpn_plob$depth)
```

## Create a post-hoc model

```{r}
model_plob <- with(rpn_plob, glm(cbind(total_count, failures) ~ groups, family = binomial))
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(model_plob, 
             linfct = mcp(groups =
                     #Is the difference between these groups different from zero?
                     c("(north.sh) - (west.sh) = 0",
                       "(north.sh) - (west.dp) = 0",
                       "(north.sh) - (se.sh) = 0",
                       "(north.sh) - (se.dp) = 0",
                       "(north.dp) - (west.sh) = 0",
                       "(north.dp) - (west.dp) = 0",
                       "(north.dp) - (se.sh) = 0",
                       "(north.dp) - (se.dp) = 0",
                       "(se.sh) - (west.sh) = 0",
                       "(se.sh) - (west.dp) = 0",
                       "(se.dp) - (west.sh) = 0",
                       "(se.dp) - (west.dp) = 0"))),
        test = adjusted("holm"))
```

```{r}
rpn_plob_bleach <- rpn_bleach %>%  
  filter(group == 'PLOB' & status == 'BL') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_plob_bleach
```

```{r}
rpn_plob_pb <- rpn_bleach %>%  
  filter(group == 'PLOB' & status == 'PB') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_plob_pb
```

```{r}
rpn_plob_pale <- rpn_bleach %>%  
  filter(group == 'PLOB' & status == 'P') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_plob_pale
```

```{r}
rpn_plob_healthy <- rpn_bleach %>%  
  filter(group == 'PLOB' & status == 'H') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_plob_healthy
```

## Pocillopora
### Generalized linear model

```{r, include = FALSE}
rpn_poci <- read.csv('rpn_cover.csv') %>%
  as_tibble() %>%
  filter(group == "POCI") %>%
  mutate_at(vars(location, depth, transect, group), factor) %>%
  mutate(
    cover = total_count/total_points,
    failures = total_points - total_count
  )
```

```{r}
rpn_poci
```

```{r}
poci.glm <- glm(cbind(total_count, failures) ~ location * depth, 
                family = binomial(link = "logit"), 
                data = rpn_poci)
```

```{r}
par(mfrow = c(2, 2))
plot(poci.glm)
```

```{r}
summary(poci.glm)
```

`Anova` function from the `car` package

```{r}
Anova(poci.glm, type = "III") # Type III because...
```

#### https://www.rpubs.com/daharo_calpoly/502695

```{r}
rpn_poci$groups <- interaction(rpn_poci$location, rpn_poci$depth)
```

## Create a post-hoc model

```{r}
model_poci <- with(rpn_poci, glm(cbind(total_count, failures) ~ groups, family = binomial))
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(model_poci, 
             linfct = mcp(groups =
                     #Is the difference between these groups different from zero?
                     c("(north.sh) - (west.sh) = 0",
                       "(north.sh) - (west.dp) = 0",
                       "(north.sh) - (se.sh) = 0",
                       "(north.sh) - (se.dp) = 0",
                       "(north.dp) - (west.sh) = 0",
                       "(north.dp) - (west.dp) = 0",
                       "(north.dp) - (se.sh) = 0",
                       "(north.dp) - (se.dp) = 0",
                       "(se.sh) - (west.sh) = 0",
                       "(se.sh) - (west.dp) = 0",
                       "(se.dp) - (west.sh) = 0",
                       "(se.dp) - (west.dp) = 0"))),
        test = adjusted("holm"))
```

```{r}
rpn_poci_bleach <- rpn_bleach %>%  
  filter(group == 'POCI' & status == 'BL') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_poci_bleach
```

```{r}
rpn_poci_pb <- rpn_bleach %>%  
  filter(group == 'POCI' & status == 'PB') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_poci_pb
```

```{r}
rpn_poci_pale <- rpn_bleach %>%  
  filter(group == 'POCI' & status == 'P') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_poci_pale
```

```{r}
rpn_poci_healthy <- rpn_bleach %>%  
  filter(group == 'POCI' & status == 'H') %>%
  group_by(location, depth, transect) %>%
  dplyr::summarise(total_count = n())
```

```{r}
rpn_poci_healthy
```

## Examine bleaching response of coral groups

### Porites

```{r}
rpn_bleach <- read.csv('rpn_coral_bleach.csv') %>%
  as_tibble() %>%
  #filter(group == "PLOB") %>%
  mutate_at(vars(location, depth, transect, species), factor) %>%
  mutate(
  bl = coral_count - bl_count,
  pb = coral_count - pb_count,
  p  = coral_count - p_count,
  h  = coral_count - h_count,
    )
```

```{r}
rpn_bleach
```

```{r}
plob_bleach <- rpn_bleach %>%
  filter(species == "plob")
```

```{r}
plob_bleach
```

```{r}
plob_pb.glm <- glm(cbind(pb_count, pb) ~ location * depth, 
                family = binomial(link = "logit"), 
                data = plob_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(plob_pb.glm)
```

```{r}
summary(plob_pb.glm)
```

`Anova` function from the `car` package

```{r}
Anova(plob_pb.glm, type = "III") # Type III because...
```

```{r}
plob_pb.aov <- Anova(plob_pb.glm, type = "III") # Type III because...
```

#### https://www.rpubs.com/daharo_calpoly/502695

```{r}
plob_bleach$groups <- interaction(plob_bleach$location, plob_bleach$depth)
```

## Create a post-hoc model

```{r}
model_plob_bleach <- with(plob_bleach, glm(cbind(pb_count, pb) ~ groups, family = binomial))
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(model_plob_bleach, 
             linfct = mcp(groups =
                     #Is the difference between these groups different from zero?
                     c("(north.sh) - (west.sh) = 0",
                       "(north.sh) - (west.dp) = 0",
                       "(north.sh) - (se.sh) = 0",
                       "(north.sh) - (se.dp) = 0",
                       "(north.dp) - (west.sh) = 0",
                       "(north.dp) - (west.dp) = 0",
                       "(north.dp) - (se.sh) = 0",
                       "(north.dp) - (se.dp) = 0",
                       "(se.sh) - (west.sh) = 0",
                       "(se.sh) - (west.dp) = 0",
                       "(se.dp) - (west.sh) = 0",
                       "(se.dp) - (west.dp) = 0"))),
        test = adjusted("holm"))
```

PLOB pale

```{r}
plob_pale.glm <- glm(cbind(p_count, p) ~ location * depth, 
                family = binomial(link = "logit"), 
                data = plob_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(plob_pale.glm)
```

```{r}
summary(plob_pale.glm)
```

`Anova` function from the `car` package

```{r}
Anova(plob_pale.glm, type = "III") # Type III because...
```

```{r}
plob_pale.aov <- Anova(plob_pale.glm, type = "III") # Type III because...
```

#### https://www.rpubs.com/daharo_calpoly/502695

```{r}
plob_bleach$groups <- interaction(plob_bleach$location, plob_bleach$depth)
```

## Create a post-hoc model

```{r}
model_plob_pale <- with(plob_bleach, glm(cbind(p_count, p) ~ groups, family = binomial))
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(model_plob_pale, 
             linfct = mcp(groups =
                     #Is the difference between these groups different from zero?
                     c("(north.sh) - (west.sh) = 0",
                       "(north.sh) - (west.dp) = 0",
                       "(north.sh) - (se.sh) = 0",
                       "(north.sh) - (se.dp) = 0",
                       "(north.dp) - (west.sh) = 0",
                       "(north.dp) - (west.dp) = 0",
                       "(north.dp) - (se.sh) = 0",
                       "(north.dp) - (se.dp) = 0",
                       "(se.sh) - (west.sh) = 0",
                       "(se.sh) - (west.dp) = 0",
                       "(se.dp) - (west.sh) = 0",
                       "(se.dp) - (west.dp) = 0"))),
        test = adjusted("holm"))
```

#### PLOB healthy 

Interaction

```{r}
plob_h.glm <- glm(cbind(h_count, h) ~ location * depth, 
                family = binomial(link = "logit"), 
                data = plob_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(plob_h.glm)
```

```{r}
summary(plob_h.glm)
```

`Anova` function from the `car` package

```{r}
Anova(plob_h.glm, type = "III") # Type III because...
```

```{r}
plob_pale.aov <- Anova(plob_h.glm, type = "III") # Type III because...
```

No interaction

```{r}
plob_h.glm2 <- glm(cbind(h_count, h) ~ location + depth, 
                family = binomial(link = "logit"), 
                data = plob_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(plob_h.glm2)
```

```{r}
summary(plob_h.glm2)
```

`Anova` function from the `car` package

```{r}
Anova(plob_h.glm2, type = "III") # Type III because...
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(plob_h.glm2, linfct = mcp(location = "Tukey")))
```

### Pocillopora

```{r}
poci_bleach <- rpn_bleach %>%
  filter(species == "poci")
```

```{r}
poci_bleach
```

#### POCI Partially Bleached

**Interaction**

```{r}
poci_pb.glm <- glm(cbind(pb_count, pb) ~ location * depth, 
                family = binomial(link = "logit"), 
                data = poci_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(poci_pb.glm)
```

```{r}
summary(poci_pb.glm)
```

`Anova` function from the `car` package

```{r}
Anova(poci_pb.glm, type = "III") # Type III because...
```

**No interaction**

```{r}
poci_pb.glm <- glm(cbind(pb_count, pb) ~ location + depth, 
                family = binomial(link = "logit"), 
                data = poci_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(poci_pb.glm)
```

```{r}
summary(poci_pb.glm)
```

`Anova` function from the `car` package

```{r}
Anova(poci_pb.glm, type = "III") # Type III because...
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(poci_pb.glm, linfct = mcp(location = "Tukey")))
```

```{r}
summary(glht(poci_pb.glm, linfct = mcp(depth = "Tukey")))
```

#### POCI Pale

```{r}
poci_pale.glm <- glm(cbind(p_count, p) ~ location * depth, 
                family = binomial(link = "logit"), 
                data = poci_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(poci_pale.glm)
```

```{r}
summary(poci_pale.glm)
```

`Anova` function from the `car` package

```{r}
Anova(poci_pale.glm, type = "III") # Type III because...
```

```{r}
poci_pale.aov <- Anova(poci_pale.glm, type = "III") # Type III because...
```

#### https://www.rpubs.com/daharo_calpoly/502695

```{r}
poci_bleach$groups <- interaction(poci_bleach$location, poci_bleach$depth)
```

## Create a post-hoc model

```{r}
model_poci_pale <- with(poci_bleach, glm(cbind(p_count, p) ~ groups, family = binomial))
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(model_poci_pale, 
             linfct = mcp(groups =
                     #Is the difference between these groups different from zero?
                     c("(north.sh) - (west.sh) = 0",
                       "(north.sh) - (west.dp) = 0",
                       "(north.sh) - (se.sh) = 0",
                       "(north.sh) - (se.dp) = 0",
                       "(north.dp) - (west.sh) = 0",
                       "(north.dp) - (west.dp) = 0",
                       "(north.dp) - (se.sh) = 0",
                       "(north.dp) - (se.dp) = 0",
                       "(se.sh) - (west.sh) = 0",
                       "(se.sh) - (west.dp) = 0",
                       "(se.dp) - (west.sh) = 0",
                       "(se.dp) - (west.dp) = 0"))),
        test = adjusted("holm"))
```

#### POCI Healthy 

Interaction

```{r}
poci_h.glm <- glm(cbind(h_count, h) ~ location * depth, 
                family = binomial(link = "logit"), 
                data = poci_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(poci_h.glm)
```

```{r}
summary(poci_h.glm)
```

`Anova` function from the `car` package

```{r}
Anova(poci_h.glm, type = "III") # Type III because...
```

```{r}
poci_pale.aov <- Anova(poci_h.glm, type = "III") # Type III because...
```

**No interaction**

```{r}
poci_h.glm2 <- glm(cbind(h_count, h) ~ location + depth, 
                family = binomial(link = "logit"), 
                data = poci_bleach)
```

```{r}
par(mfrow = c(2, 2))
plot(poci_h.glm2)
```

```{r}
summary(poci_h.glm2)
```

`Anova` function from the `car` package

```{r}
Anova(poci_h.glm2, type = "III") # Type III because...
```

## Determine the post-hoc comparisons of interest

```{r}
summary(glht(poci_h.glm2, linfct = mcp(location = "Tukey")))
```

```{r}
summary(glht(poci_h.glm2, linfct = mcp(depth = "Tukey")))
```
